 \documentclass[margin,line,pifont,palatino,courier]{res}

\usepackage{pifont}
\usepackage[latin1] { inputenc}

\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	filecolor=magenta,      
	urlcolor=blue,
}

\usepackage{longtable}

\usepackage{soul}

\usepackage{booktabs}

\usepackage{changepage}



 \textheight=9.0in
\usepackage{fancyhdr}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\fancyhf{}
\rfoot{\footnotesize \today}
\cfoot{{\footnotesize \thepage /10 }}
\lfoot{{\footnotesize Kristen Aiemjoy, PhD MSc }}



\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

\begin{document}

	






\begin{flushright}
{\huge \textbf {Kristen Aiemjoy, PhD, MSc }}  \\
\vspace{.1in}
  \href {kaiemjoy@ucdavis.edu}{kaiemjoy@health.ucdavis.edu} \\

\end{flushright}
















\section{\sc Positions}

\begin{tabular}{p{4.2in}r}
         Assistant Professor   &  Oct 2021 -\\
	\textbf {University of California Davis School of Medicine}   \\
    {\bf Division of Epidemiology}\\
        {\bf Department of Public Health Sciences}\\
\end{tabular}

\begin{tabular}{p{4.2in}r}
	Adjunct Assistant Professor   &  Jan 2023 -\\
	\textbf {Mahidol University Faculty of Tropical Medicine}   \\
	{\bf Department of Microbiology and Immunology}\\
		{\bf Bangkok, Thailand}\\
\end{tabular}


\begin{tabular}{p{4.2in}r}
	Visiting Scientist   &  June 2022 -\\
	\textbf {Mahidol Oxford Tropical Medicine Research Unit}   \\
	{\bf  Epidemiology Unit}\\
	{\bf Bangkok, Thailand}\\
\end{tabular}

\begin{tabular}{p{4.2in}r}
         Postdoctoral Research Fellow   &   2018 - 2021\\
	\textbf {Stanford University School of Medicine}   \\
    {\bf Division of Infectious Diseases and Geographic Medicine}\\
\end{tabular}


\section{\sc Education}


\begin{tabular}{p{4.2in}r}
{\bf University of California San Francisco} & 2013 - 2018 \\
{\textit {PhD Epidemiology} }
\end{tabular}

\begin{tabular}{p{4.2in}r}
{\bf London School of Hygiene and Tropical Medicine   } & 2010 - 2011 \\
{\textit {MSc Public Health} }
\end{tabular}

\begin{tabular}{p{4.2in}r}
{\bf Georgetown University, Walsh School of Foreign Service	   }  & 2006 - 2010 \\
{\textit {BSc Foreign Service \& Global health, Cum Laude} }
\end{tabular}



\section{\sc Publications}

Saiprom N, Nimnuan-ngam S, Phunpang R, Schildhauer SH, Morrison E, Tandhavanant S, Chandna A, Sengyee S, West TE, Burtnick MN, Brett PJ, Chantratita N, \textbf{Aiemjoy K}. \href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=5312903}{Longitudinal Profiling of Antibody Responses to \textit{Burkholderia pseudomallei}: Implications for Diagnosis and Surveillance} \textit{SSRN Preprint}. 2025 Jun 23.


Lai KW, Orwa C, Seidman JC, Garrett DO, Saha SK, Tamrakar D, Qamar FN, Charles R, Andrews JR, \textbf{Aiemjoy K}, et al. \href{ https://pubmed.ncbi.nlm.nih.gov/40502584/}{serocalculator, an R package for estimating seroincidence from cross-sectional serological data} \textit{medRxiv}. 2025 Jun.

Tamrakar D, Naga S, Jung E, Shrestha B, Bista Roka P, Pokharel RS, Shah SB, Bajracharya AT, Mahadup S, Katuwal N, et al. \href{ https://www.medrxiv.org/content/medrxiv/early/2025/06/18/2025.06.17.25329748.full.pdf}{Impact of the COVID-19 pandemic and typhoid conjugate vaccine introduction on typhoid fever in Nepal} \textit{medRxiv}. 2025 Jun.

Khan A, Kamenskaya P, Rezende I, Mutuku F, Ndenga BA, Jembe Z, Maina P, Chebii P, Ronga C, Okuta V, et al. \href{ https://www.medrxiv.org/content/10.1101/2025.06.24.25330223v1}{Seroincidence rate of typhoidal Salmonella in children in Kenya} \textit{medRxiv}. 2025 Jun.

Seidman JC, \textbf{Aiemjoy K}, Adnan M, Dehraj IF, Iqbal J, Iqbal K, Irfan S, Islam N, Kabir MS, Katuwal N, et al. \href{ https://www.medrxiv.org/content/10.1101/2025.06.20.25329792v1}{Evaluating the accuracy of Salmonella Typhi Hemolysin E and lipopolysaccharide IgA to discriminate enteric fever from other febrile illnesses in South Asia} \textit{medRxiv}. 2025 Jun.

	Kamau E, Ante-Testard PA, Gwyn S, Blumberg S, Abdalla Z, \textbf{Aiemjoy K}, Amza A, Aragie S, Arzika AM, Awoussi MS, et al. \href{ https://www.nature.com/articles/s41467-025-60581-z}{Characterizing trachoma elimination using serology} \textit{Nature Communications}. 2025 Jan.

	  Abraham D, Kathiresan L, Sasikumar M, \textbf{Aiemjoy K}, Charles RC, Kumar D, Srinivasan R, Troman C, Gray E, Uzzell CB, John J, Veeraraghavan B, Grassly NC, Mohan VR. \href{10.1371/journal.pntd.0012373} {Wastewater surveillance for Salmonella Typhi and its association with seroincidence of enteric fever in Vellore, India}. \textit{PLoS Negl Trop Dis}. 2025 Mar 3;19(3):e0012373.  PMID: 40029872

	Kutawal N, Thapa M, Shrestha S, Vaidya K, Bogoch II, Shrestha R, Tamrakar D, Andrews JR, \textbf{Aiemjoy K}. \href{https://journals.plos.org/plosntds/article?id=10.1371/journal.pntd.0012375}{Hepatitis E Virus in Kathmandu Valley: Insights from a Representative Longitudinal Serosurvey} \textit{PloS NTD}. 2024 Aug 05. PMID: 39102451
	
	\textbf{Aiemjoy K}, Kutawal N, Vaidya K, Shrestha S, Thapa M, Teunis P, Bogoch II, Trowbridge P, Kantipong P, Blacksell SD, Varghese GM, Maude R, Tamrakar D, Andrews JR. \href{https://doi.org/10.4269/ajtmh.23-0475}{Estimating the seroincidence of scrub typhus using antibody dynamics following infection.} \textit{Am J Trop Med Hyg}. 2024 Jun 11;  PMID: 38861980.
	
	Shrestha S, da Silva K, Shakya J, Yu AT, Kutawal N, Shrestha R, Shakya M, Shahi SB, Naga SR, LeBoa C, \textbf{Aiemjoy K}, Bogoch I, Saha S, Tamrakar D, Andrews JR. \href{https://www.medrxiv.org/content/10.1101/2023.02.14.23285806v1}{Detection of Salmonella Typhi bacteriophages in surface waters as a scalable approach to environmental surveillance.} \textit{PLoS Negl Trop Dis}. 2024; 18(2): e0011912.
	
	Looareesuwan P, \textbf{Aiemjoy K}, Charoensakulchai S, Thaipadungpanit J, Wongsantichon J, Tanganuchitcharnchai A, Rungrojn A, Blacksell SD, Matsee W. \href{https://academic.oup.com/jtm/advance-article/doi/10.1093/jtm/taad143/7413193#google_vignette}{Diagnostic challenges and antibody kinetics in a paediatric traveller with scrub typhus.} \textit{J Travel Med}. 2023 Dec 28;30(8): taad143. PMID: 37952213.
	
	LeBoa C, Shrestha S, Shakya J, Naga SR, Shrestha S, Shakya M, Yu AT, Shrestha R, Vaidya K, Katuwal N, \textbf{Aiemjoy K}, Bogoch I, Uzzell CB, Garrett D, Luby SP, Andrews JR, Tamrakar D. \href{https://journals.plos.org/plosntds/article?id=10.1371/journal.pntd.0011341}{Environmental surveillance for typhoidal Salmonellas in household and surface waters in Nepal identifies potential transmission pathways.} \textit{PLoS Negl Trop Dis}. 2023; 17(10): e0011341. PMID: 37851667
	
	Teunis P, Wang Y, \textbf{Aiemjoy K}, Kretzschmar M, Aerts M. \href{https://onlinelibrary.wiley.com/doi/10.1002/sim.9906}{Estimating seroconversion rates accounting for repeated infections by approximate Bayesian computation.} \textit{Stat Med}. 2023 Sep 27;42(28):5160-5188.  PMID: 37277341.
	
	Tedijanto C, Solomon AW, Martin DL, Nash SD, Keenan JD, Lietman TM, Lammie PJ, \textbf{Aiemjoy K}, Amza A, Aragie S, Arzika AM. \href{https://www.nature.com/articles/s41467-023-38940-5}{Monitoring transmission intensity of trachoma with serology.} \textit{Nat Commun}. 2023 Jun 5;14(1):3269.  PMID: 37277341.
	
	\textbf{Aiemjoy K}, Seidman JC, Charles RC, Andrews JR. \href{https://academic.oup.com/ofid/article/10/Supplement_1/S21/7188899}{Seroepidemiology for enteric fever: emerging approaches and opportunities.} \textit{Open Forum Infect Dis}. 2023 Jun 2;10(Suppl 1):S21-S25.  PMID: 37274530.
	
	\textbf{Aiemjoy K}, Rumunu J, Hassen JJ, Wiens KE, Garrett D, Kamenskaya P, Harris JB, Azman AS, Teunis P, Seidman J, Wamala JF, Andrews JR, Charles RC. \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC9622235/}{Seroincidence of Enteric Fever in Juba, South Sudan.} \textit{Emerg Infect Dis}. 2022 Nov 28;28(11):2316-2320.  PMID: 36286224.
	
	\textbf{Aiemjoy K}, Seidman JC, Saha S, Munira SJ, Islam MS, Sarkar A, Alam N, Tamrakar D, Vaidya K, Shrestha R, Shakya J, Katuwal N, Shrestha S, Yousafzai MT, Iqbal J, Dehraj IF, Maria N, Adnan M, Pervaiz S, Carter AS, Longley AT, Fraser C, Ryan ET, Nodoushani A, Fasano A, Leonard MM, Kenyon V, Bogoch II, Jeon HJ, Haselbeck A, Park SE, Zellweger RM, Marks F, Owusu-Dabo E, Adu-Sarkodie Y, Owusu M, Teunis P, Luby SP, Garrett DO, Qamar FN, Saha SK, Charles RC, Andrews JR. \href{https://www.thelancet.com/journals/lanmic/article/PIIS2666-5247(22)00114-8/fulltext}{Estimating typhoid incidence from community-based serosurveys: a multicohort study.} \textit{Lancet Microbe}. 2022 Jun 21;3(8):e578-e587.  PMID: 35714648.
	
	Garrett D, Longley A, \textbf{Aiemjoy K}, Qamar FN, Saha SK, Yousafzai MT, Hemlock C, Yu A, Vaidya K, Tamrakar D, Saha S, Bogoch I, Bern C, Date K, Saha S, Islam MS, Sayeed I, Shakoor S, Dehraj I, Mehmood J, Sajib M, Islam M, Thobani R, Hotwani A, Rehman NU, Irfan S, Naga S, Memon A, Pradhan S, Iqbal K, Shrestha R, Rahman H, Hasan MM, Qazi S, Kazi AM, Saddal N, Syed JR, Hunzai M, Marks F, Seidman J, Carter AS, Andrews JR, Luby S. \href{https://www.thelancet.com/journals/langlo/article/PIIS2214-109X(22)00119-X/fulltext}{Incidence of Typhoid and Paratyphoid Fever in Bangladesh, Nepal, and Pakistan: Results of the Surveillance for Enteric Fever in Asia Project.} \textit{Lancet Glob Health}. 2022 Jul;10(7):e978-e988.  PMID: 35714648.
	
	Aragie S, Wittberg DM, Tadesse W, Dagnew A, Hailu D, Chernet A, Melo JS, \textbf{Aiemjoy K}, Haile M, Zeru T, Tadesse Z, Gwyn S, Martin DL, Arnold BF, Freeman MC, Nash SD, Callahan EK, Porco TC, Lietman TM, Keenan JD. \href{https://www.sciencedirect.com/science/article/pii/S2214109X21004095}{Water, sanitation, and hygiene for control of trachoma in Ethiopia (WUHA): a two-arm, parallel-group, cluster-randomised trial.} \textit{Lancet Glob Health}. 2022 Jan;10(1):e87-e95.  PMID: 34919861.
	
	Aragie S, Gebresillasie S, Chernet A, Shiferaw A, Tadesse Z, Zerihun M, Varnado NE, Cotter SY, Wittberg DM, Zhou Z, Callahan EK, Nash SD, \textbf{Aiemjoy K}, Keenan JD. \href{https://www.ajtmh.org/view/journals/tpmd/aop/article-10.4269-ajtmh.20-0390/article-10.4269-ajtmh.20-0390.xml}{Community Hand-Dug Wells for Trachoma: A Cluster-Randomized Trial.} \textit{Am J Trop Med Hyg}. 2021 Apr 7;104(4):1340-1345. PMID: 33720957.
	
	Fry D, Aragie S, Tadesse W, Melo JS, \textbf{Aiemjoy K}, Chanyalew M, Emmerson P, Freeman MC, Nash SD, Callahan EK, Tadesse Z, Zerihun M, Porco TC, Lietman TM, Keenan JD. \href{https://bmjopen.bmj.com/content/11/2/e039529}{WASH Upgrades for Health in Amhara (WUHA): study protocol for a cluster-randomised trial in Ethiopia.} \textit{BMJ Open}. 2021 Feb 25;11(2):e039529.  PMID: 33632728.
	
	\textbf{Aiemjoy K}, Naga S, Qamar FN, Saha S, Tamrakar D, Yu AT, Garrett D, Luby SP, Andrews JR, Bogoch II. \href{https://doi.org/10.1093/cid/ciaa1297}{Diagnostic value of clinical features to distinguish enteric fever from other febrile illnesses in Bangladesh, Nepal, and Pakistan.} \textit{Clin Infect Dis}. 2020 Nov 23;71(Supplement 3):S275-S282.  PMID: 32930683.
	
	Vaidya K, \textbf{Aiemjoy K}, Qamar FN, Saha S, Tamrakar D, Barkume C, Garrett D, Luby SP, Andrews JR. \href{https://academic.oup.com/cid/article/71/Supplement_3/S285/6013563?login=true}{Antibiotic use prior to hospital presentation among individuals with suspected enteric fever in Nepal, Bangladesh and Pakistan.} \textit{Clin Infect Dis}. 2020 Nov 23;71(Supplement 3):S285-S292.  PMID: 32930694.
	
	Tamrakar D, Vaidya K, Yu AT, \textbf{Aiemjoy K}, Naga SR, Cao Y, Bern C, Qamar FN, Saha S, Date KA, Longley AT, Hemlock C, Luby SP, Garrett DO, Bogoch II, Andrews JR. \href{https://doi.org/10.1093/cid/ciaa1319}{Spatial heterogeneity of enteric fever in two diverse communities in Nepal.} \textit{Clin Infect Dis}. 2020 Nov 23;71(Supplement 3):S273-S282.  PMID: 32930692.
	
	Yu AT, Shakya R, Tamrakar D, Vaidya K, Maples S, Date K, Bogoch II, Bern C, Garrett D, Luby SP, \textbf{Aiemjoy K}, Andrews JR. \href{https://doi.org/10.1093/cid/ciaa1310}{A cluster-based, spatial-sampling method for assessing household healthcare utilization patterns in resource-limited settings.} \textit{Clin Infect Dis}. 2020 Nov 23;71(Supplement 3):S293-S300. PMID: 32930695.
	
	Andrews JR, Vaidya K, Saha S, Yousafzai MT, Hemlock C, Longley A, \textbf{Aiemjoy K}, Yu AT, Bogoch I, Tamrakar D, Date K, Saha S, Garrett D, Luby SP, Qamar F. \href{https://doi.org/10.1093/cid/ciaa1321}{Healthcare Utilization Patterns for Acute Febrile Illness in Bangladesh, Nepal, and Pakistan: Results from the Surveillance for Enteric Fever in Asia Project.} \textit{Clin Infect Dis}. 2020 Nov 23;71(Supplement 3):S285-S300.  PMID: 32930696.
	
	\textbf{Aiemjoy K}, Aragie S, Wittberg DM, Tadesse Z, Callahan EK, Gwyn S, Martin D, Keenan JD, Arnold BF. \href{https://doi.org/10.1371/journal.pntd.0008647}{Seroprevalence of antibodies against Chlamydia trachomatis and enteropathogens and distance to the nearest water source among young children in the Amhara Region of Ethiopia.} \textit{PLoS Negl Trop Dis}. 2020 Sep 10;14(9): e0008647. doi: 10.1371/journal.pntd.0008647. PMID: 32877398.
	
	\textbf{Aiemjoy K}, Arzika AM, Cook C, Lebas E, Pilotte N, Grant JR, Williams SA, Lietman TM, Keenan JD. \href{https://gatesopenresearch.org/articles/4-38}{Molecular detection of intestinal helminths and protozoa among young children in Dosso Region, Niger.} \textit{Gates Open Res}. 2020 Aug 28;4:38.  PMID: 32923983.
	
	Andrews JR, Yu AT, Saha S, Shakya J, \textbf{Aiemjoy K}, Horng L, Qamar F, Garrett D, Baker S, Saha S, Luby SP. \href{https://doi.org/10.1093/cid/ciaa513}{Environmental Surveillance as a Tool for Identifying High-risk Settings for Typhoid Transmission.} \textit{Clin Infect Dis}. 2020 Apr 29;71(Supplement 2):S153-S158.  PMID: 32239192.
	
	Carey ME, MacWright WR, Im J, Meiring JE, Gibani MM, Park SE, Longley A, Jeon HJ, Hemlock C, Yu AT, Soura A, \textbf{Aiemjoy K}, Owusu-Dabo E, et al. \href{https://doi.org/10.1093/cid/ciaa367}{The Surveillance for Enteric Fever in Asia Project (SEAP), Severe Typhoid Fever Surveillance in Africa (SETA), Surveillance of Enteric Fever in India (SEFI), and Strategic Typhoid Alliance Across Africa and Asia (STRATAA) Population-based Enteric Fever Studies: A Review of Methodological Similarities and Differences.} \textit{Clin Infect Dis}. 2020 Apr 15;71(Supplement 2):S285-S292.  PMID: 32930694.
	
	Maasch JR, Arzika AM, Cook C, Lebas E, Pilotte N, Grant JR, Williams SA, Keenan JD, Lietman TM, \textbf{Aiemjoy K}. \href{https://doi.org/10.4269/ajtmh.19-0909}{Rectal swabs as an alternative sample collection method to bulk stool for the real-time PCR detection of Giardia duodenalis.} \textit{Am J Trop Med Hyg}. 2020 Sep;103(3):1276-1282.  PMID: 33020665.
	
	Aragie S, Wittberg DM, \textbf{Aiemjoy K}, Melo JS, Smith MJ, Nash SD, Tadesse Z, Keenan JD. \href{https://doi.org/10.1093/trstmh/traa039}{Odour reduction interventions for simple pit latrines in rural Ethiopia: a randomized study.} \textit{Trans R Soc Trop Med Hyg}. 2020 Oct;114(10):743-752. PMID: 32833621.
	
	\textbf{Aiemjoy K}, Atlan E, Aragie S, Gebresillasie S, Fry D, Dagnew A, Hailu D, Chanyalew M, Tadesse Z, Callahan K, Delwart E, Keenan JD. \href{https://doi.org/10.1186/s12879-019-3674-3}{Differences in the pediatric enteric virome across watery, loose and formed stool consistency types.} \textit{BMC Infect Dis}. 2019 Jan 14;19(1):53.  PMID: 30642268.
	
	Keenan JD, Gebresillasie S, Stoller NE, Ayele B, Tadesse Z, Cotter S, Ray K, \textbf{Aiemjoy K}, Porco T, Callahan K, Emerson PM, Lietman T. \href{https://doi.org/10.1371/journal.pntd.0007442}{Linear growth in preschool children treated with mass azithromycin distributions for trachoma: A cluster-randomized trial.} \textit{PLoS Negl Trop Dis}. 2019 Jun 5;13(6):e0007442.  PMID: 31170247.
	
	Atlan E, \textbf{Aiemjoy K}, Phan T, Deng X, Aragie S, Tadesse Z, Callahan K, Keenan JD, Delwart E. \href{https://doi.org/10.1371/journal.pone.0202054}{Enteric viromes of Ethiopian children participating in a clean water intervention trial.} \textit{PLoS One}. 2018 Aug 21;13(8):e0202054.  PMID: 30138475.
	
	\textbf{Aiemjoy K}, Aragie S, Gebresillasie S, Fry D, Dagnew A, Hailu D, Chanyalew M, Tadesse Z, Stewart A, Callahan K, Freeman M, Neuhaus J, Arnold B, Keenan JD. \href{https://www.ajtmh.org/content/journals/10.4269/ajtmh.17-0806}{Defining Diarrhea: A population-based validation study of caregiver-reported stool consistency in the Amhara region of Ethiopia.} \textit{Am J Trop Med Hyg}. 2018 Apr;98(4):1013-1020. PMID: 29436359.
	
	\textbf{Aiemjoy K}, Gebresillasie S, Stoller NE, Shiferaw A, Tadesse Z, Chanyalew M, Aragie S, Callahan K, and Keenan JD. \href{https://www.ajtmh.org/content/journals/10.4269/ajtmh.16-0800}{Epidemiology of Soil-Transmitted Helminth and Intestinal Protozoan Infections in Preschool-Aged Children in the Amhara Region of Ethiopia.} \textit{Am J Trop Med Hyg}. 2017 Apr;96(4):866-872. PMID: 28167597.
	
	\textbf{Aiemjoy K}, Stoller NE, Gebresillasie S, Shiferaw A, Tadesse Z, Sewent T, Ayele B, Chanyalew M, Aragie S, Callahan K, Stewart A, Emerson PM, Lietman TM, Keenan JD, Oldenburg CE. \href{https://www.ajtmh.org/content/journals/10.4269/ajtmh.16-0541}{Is Using a Latrine 'A Strange Thing To Do'? A Mixed-Methods Study of Sanitation Preference and Behaviors in Rural Ethiopia.} \textit{Am J Trop Med Hyg}. 2017 Jan;96(1):65-73.  PMID: 27800585.
	
	\textbf{Aiemjoy K}, Stoller NE, Gebresillasie S, Shiferaw A, Tadesse Z, Sewent T, Ayele B, Chanyalew M, Callahan K, Stewart A, Emerson PM, Lietman TM, Keenan JD, Oldenburg CE. \href{https://journals.plos.org/plosntds/article?id=10.1371/journal.pntd.0005099}{'If an Eye Is Washed Properly, It Means It Would See Clearly': A Mixed Methods Study of Face Washing Knowledge, Attitudes, and Behaviors in Rural Ethiopia.} \textit{PLoS Negl Trop Dis}. 2016 Oct;10(10):e0005099.  PMID: 27741320.
	
	Irish SR, \textbf{Aiemjoy K}, Torondel B, Abdelahi F, Ensink JH. \href{https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0067951}{Characteristics of latrines in central Tanzania and their relation to fly catches.} \textit{PLoS One}. 2013 Jul 10;8(7):e67951.  PMID: 23819098.
	
%\newpage


\section{\sc Invited Presentations}

Antibody responses to HlyE suggest high burden of typhoidal Salmonella infections in rural Niger. \textit{Typhoid Vaccine Acceleration Consortium Annual Meeting} (Blantyre, Malawi); July 17, 2025.

Population-based serosurveillance for enteric fever: methodological overview and new findings from Cambodia and Afghanistan. \textit{Typhoid Vaccine Acceleration Consortium Annual Meeting} (Blantyre, Malawi); July 17, 2025.

Estimating seroincidence. \textit{2nd Summit on Integrated Multiplex Serosurveillance} (Lilongwe, Malawi); May 27, 2025.

Preliminary Enteric Fever Seroincidence Estimates from SEACTN-Cambodia. \textit{Cambodian Ministry of Health} (Virtual); November 11, 2024.

Leveraging antibody decay dynamics to characterize the population-level force of infection. \textit{UCLH Division of Infection} (Virtual); July 10, 2024.

Out of Sight, Top of Mind: A Pediatric Traveler's Hidden Scalp Eschar and its Implications for Scrub Typhus Exposure in Western Thailand. \textit{American Society for Rickettsiology Spotlight on Rickettsia} (Virtual); January 2024.

Seroepidemiology to inform and evaluate Typhoid Vaccine Introduction. \textit{Vaccinology in Developing Countries Short Course} (Aga Khan University, Pakistan - presented virtually); January 11, 2023.

A new serologic approach for estimating the population-level incidence of scrub typhus. \textit{Joint International Tropical Medicine Meeting} (Bangkok, Thailand); December 2022.

Leveraging antibody decay kinetics to understand infection transmission. \textit{Mahidol University Faculty of Tropical Medicine, Department of Microbiology and Immunology} (Bangkok, Thailand); September 23, 2022.

Leveraging antibody dynamics to estimate the seroincidence of scrub typhus. \textit{NIH-MORU Scrub Typhus Symposium} (Bangkok, Thailand); September 15, 2022.

Estimating typhoid incidence from community-based serosurveys.
\begin{list1}
	\item[-] Mahidol Oxford Tropical Medicine Research Unit (Bangkok, Thailand); June 27, 2022.
	\item[-] Assumption University, Department of Biotechnology (Bangkok, Thailand); July 11, 2022.
	\item[-] Chiang Mai University, Department of Microbiology (Chiang Mai, Thailand); August 18, 2022.
	\item[-] Manmohan Memorial Institute of Health Sciences (MMIHS) (Kathmandu, Nepal); September 12, 2022.
\end{list1}

Enteric Fever Incidence Estimates from the Sero-Epidemiology and Environmental Surveillance Study in Nepal, Pakistan and Bangladesh. Stakeholder consultation to review and interpret emerging data on enteric fever disease burden. \textit{The World Health Organization, Department of Immunization, Vaccines and Biologicals} (Virtual); May 2021.

Defining Diarrhea: Challenges With Symptomatic Reporting and Potential Alternatives. \textit{Diarrhea Innovations Working Group} (Virtual); December 2019.


 

\section{\sc Scientific Conference Presentations}


Scrub typhus: A significant and underrecognized cause of acute febrile illness in Kathmandu. American Society of Tropical Medicine and Hygiene. Toronto, Canada; November 2025

Saiprom N*, Nimnuan-ngam S, Phunpang R, Schildhauer S H, Morrison E, Tandhavanant S, West T E, Burtnick M, Burtnick P, Chantratita N, \textbf{Aiemjoy K}. Modeling antibody decay to strengthen melioidosis surveillance and diagnostic tools. American Society of Tropical Medicine and Hygiene Annual Meeting; Toronto, Canada; November 2025.

Pediatric Scrub Typhus in Urban Kathmandu: Findings from One Year of Prospective Clinical Surveillance. Asia Pacific Rickettsia Conference 4. Penang Malaysia; September 2025

Spatiotemporal and Climatic Pattern of Pediatric Scrub Typhus in Kathmandu, Nepal. Asia Pacific Rickettsia Conference 4. [Oral Presentation] Penang, Malaysia; September 2025

Exploring routes of exposure and risk factors for scrub typhus in children: A qualitative study in Nepal. [Poster Presentation] Penang Malaysia; September 2025

Naga SR*, Shahi SB, Goshain S, Maharjan M, Katuwal N, Shrestha R, Andrews JR, Tamrakar D, \textbf{Aiemjoy K}. Characterizing the burden of scrub typhus in Nepalese children: A school-based serosurveillance approach. \textit{American Society of Tropical Medicine and Hygiene Annual Meeting}; New Orleans, LA; November 2024.

\textbf{Aiemjoy K}, Seidman JC, Arzika AM, Lai KWJ, Maliki R, Abdou A, Garrett D, Munroe C, Gonzalez A, Sukri L, Lebas E, Cook C, Arnold BF, Lietman TM, Neuzil KM, Andrews JR, Keenan JD, Charles RC. Effect of biannual azithromycin MDA on enteric fever transmission intensity in Niger. \textit{American Society of Tropical Medicine and Hygiene Annual Meeting}; New Orleans, LA; November 2024.


\textbf{Aiemjoy K} \& Morrison DE. An open-source R package for estimating seroincidence from cross-sectional serosurveys. \textit{Gates Foundation Infectious Disease Modeling (IDM) Symposium}; Seattle, WA; October 2024.

\textbf{Aiemjoy K}, John J, Charles R, Teunis P, Andrews JR. Seroepidemiology for evaluating the impact of typhoid vaccine interventions. \textit{Coalition Against Typhoid}; Kigali, Rwanda; December 2023.


 \textbf {Aiemjoy K}. Latest advances in seroepidemiology for enteric fever. \textit{Coalition Against Typhoid}; Kigali, Rwanda; December 2023.

	\textbf{Aiemjoy K}, Kutawal N, Vaidya K, Shrestha S, Thapa M, Teunis P, Bogoch II, Trowbridge P, Kantipong P, Blacksell SD, Varghese GM, Maude R, Tamrakar D, Andrews JR. Estimating the seroincidence of scrub typhus using antibody dynamics following infection. \textit{The American Society of Tropical Medicine and Hygiene}; Chicago, IL, USA; October 2023.

 \textbf {Aiemjoy K}. Evaluating diagnostic thresholds for pediatric scrub typhus. \textit{Asia-Pacific Rickettsia Conference}; Mahabalipuram, Chennai, India; September 2023.


 \textbf {Aiemjoy K}. Evaluating the accuracy of novel antigens for diagnosing enteric fever in Bangladesh, Nepal, and Pakistan. \textit{The American Society of Tropical Medicine and Hygiene}; Seattle, WA, USA; November 2023.

 \textbf {Aiemjoy K}. Leveraging longitudinal antibody kinetics to derive enteric fever incidence estimates in population-based samples. \textit{Coalition Against Typhoid}; Virtual; December 2021.

 \textbf {Aiemjoy K}. Pivoting in a pandemic: Serologic surveillance for enteric fever. \textit{The American Society of Tropical Medicine and Hygiene}; Virtual; November 2021.

 \textbf {Aiemjoy K}. The sero-epidemiology and environmental surveillance study in Nepal, Pakistan, and Bangladesh: Methods and preliminary results. \textit{The American Society of Tropical Medicine and Hygiene}; Virtual; November 2020.

\textbf {Aiemjoy K}, Aragie S, Fry D, Tadesse Z, Callahan EK, Gwyn S, Martin D, Keenan  JD, Arnold B. Seroprevalence of antibodies against \textit{Chlamydia trachomatis} and enteropathogens and distance to the nearest water source among young children in the Amhara Region of Ethiopia. \textit{The American Society of Tropical Medicine and Hygiene}; Washington, DC; November 2019.

\textbf {Aiemjoy K}, Aragie S, Gebresillasie S, Fry D, Dagnew A, Hailu D, Chanyalew M, Tadesse Z, Stewart A, Callahan K, Freeman M, Neuhaus J, Arnold B, Keenan JD. Defining diarrhea: A population-based validation study of caregiver-reported stool consistency in the Amhara region of Ethiopia. \textit{The American Society of Tropical Medicine and Hygiene}; New Orleans, LA; October 2018.

\textbf {Aiemjoy K}, Aragie S, Gebresillasie S, Fry D, Chanyalew M, Hailu D, Tadesse Z, Stewart A, Callahan K, Freeman M, Arnold BF, Keenan JD. Evaluating the validity of caregiver-reported diarrhea: A large, population-based study in the Amhara region of Ethiopia. \textit{Society for Epidemiologic Research}; Seattle, WA; June 2017.


\section{\sc Conference Symposiums and workshops}

\textbf{Aiemjoy K}, Seidman J. Closing the typhoid surveillance gap: Operationalizing novel surveillance methods to describe enteric fever burden and support vaccine decision-making. \textit{American Society of Tropical Medicine and Hygiene Annual Meeting}; New Orleans, LA; November 2024.

\textbf{Aiemjoy K}, Seidman J, Morrison E, Charles RC, Wen-Jeh K. Conference Workshop: Estimating enteric fever seroincidence rates in R. \textit{Coalition Against Typhoid}; Kigali, Rwanda; December 2023.

\textbf{Aiemjoy K}, Charles RC, Grassly N. Symposium: Bridging the Gap: Environmental and sero-surveillance for estimating typhoid burden. \textit{Coalition Against Typhoid}; Kigali, Rwanda; December 2023.

*Mentee


\section{\sc Grants and Fellowships}

\begin{longtable}{p{4.2in}r}
	\textbf{Current}\\
\addlinespace

National Institute of Health (NIH) National Institute for Allergy and Infectious Diseases (NIAID) &  2024 - 2029 \\
R01-AI181283: \textit{Novel tools for measuring typhoid vaccine impact} &\\
Role: Co-I & \\
\addlinespace

National Institute of Health (NIH) Fogarty International Center & 2022 - 2027 \\
International Research Scientists Development Award (K01) & \\
K01-TW012177: \textit{Estimating the Seroincidence of Melioidosis, Typhoid Fever and Scrub Typhus from
	Cross-sectional Serosurveys} &\\
Role: PI & \\
\addlinespace


	U.S.-Japan Cooperative Medical Sciences Award & 2023 - 2025 \\
	National Institute of Allergy and Infectious Diseases (NIAID) and CRDF Global  \\
	\textit{Characterizing Longitudinal Antibody Dynamics After Scrub Typhus Infection in Kathmandu, Nepal and Chiang Rai, Thailand} & \\
	Role: Co-PI & \\
	\addlinespace
	
	
	
	Bill and Melinda Gates Foundation  & 2022 - 2025 \\
	\textit{Support for use of Enteric Fever Serological Tools} & \\
	Role: Co-Investigator (PI: R. Charles, Mass General Hospital) & \\
	\addlinespace
	
	
	\addlinespace
	\textbf{Completed}\\
	\addlinespace
	
  National Institute of Health (NIH) National Institute for Allergy and Infectious Diseases (NIAID) &  2023 - 2025 \\
  R21-AI176416: \textit{Serocalculator: Estimating Incidence Rates from Serological Data} &\\
  Role: MPI & \\
  \addlinespace


	Bill and Melinda Gates Foundation  & 2022 - 2025 \\
	\textit{Inform decision-making for enteric fever control and prevention} & \\
	Role: Co-Investigator (PI: D. Garrett, Sabin Vaccine Institute)& \\
	\addlinespace
	
	PATH - Bill and Melinda Gates Foundation  & 2022 - 2024 \\
	\textit{Cambodia Enteric Fever Serosurveillance Projec}  \\
	Role: PI) \\
	\addlinespace
	
  UC Davis Global Affairs Seed Grant  & 2023 - 2024  \\
  \textit{Pediatric Scrub Typhus in Nepal: a new research collaboration with Kanti Children's Hospital} &\\
  Role: PI & \\
  \addlinespace

	National Institute of Health (NIH) Loan repayment program & 2019 - 2024 \\
	National Institute of Allergy and Infectious Diseases (NIAID) & \\
	Role: PI & \\
	\addlinespace
	
	UC Davis COVID-19 Research Accelerator FundingTrack (CRAFT) 2.0 Program  & 2023  \\
	\textit{Enteric Fever Burden in Rural Southeast Asia} &\\
	Role: PI & \\
	\addlinespace
	
	UC Davis Academic Senate Research Grant  & 2022  \\
	Role: PI & \\
	\addlinespace
	
	National Institute of Health (NIH) F31  & 2016 - 2018 \\
	National Institute of Child Health and Development & \\
	\textit{Quantitative bias analysis to adjust for misclassified pediatric diarrhea in a cluster randomized trial} & \\
	Role: PI\\
	\addlinespace
	
	
	UCSF Resource Allocation Program Catalyst Award & 2017 - 2018 \\
	\textit{A new low-cost method for detecting soil-transmitted helminth infections in young children} \\
	Role: Co-PI \\
	\addlinespace
	
	Stanford Center for Innovation in Global Health (CIGH) Seed Grant &  2019 - 2021\\
	\textit{Integrated serologic surveillance for infectious disease transmission and vaccine-acquired immunity by finger-stick dried blood spots} & \\
	Role: PI & \\
	\addlinespace
	

	
\end{longtable}


\section{\sc Additional Research Experience}
 
     

 
  

   \begin{tabular}{p{4.6in}r}
	Epidemiologist &  2013 \\
	\textbf {M\'edecins Sans Fronti\'eres} \\
	\textit {South Sudan} \\ 


\addlinespace
	Assistant Director & 2012 \\
	\textbf {Area Health Education Center, University of Hawaii} \\ 
	\textit {Hawaii and US-Affiliated Pacific Islands} \\ 


	
\addlinespace
	Epidemiologist, intern & 2011 \\
	\textbf {World Health Organization} \\
	\textit {Denmark} \\ 
	
	\end{tabular}
\begin{tabular}{p{4.6in}r}
	
\addlinespace
	Graduate Student Researcher &  2011 \\
	\textbf {Ifakara Health Institute} \\
	\textit {Tanzania} \\ 

\addlinespace
	Student Researcher &  2011 \\
	\textbf {The AIDS Support Organization (TASO)} \\
	\textit {Uganda} \\  
	\end{tabular}
       


\section{\sc Honors and Awards}
\begin{tabular}{p{4.6in}r}
	Coalition Against Typhoid, Female Leader in Typhoid & 2024 \\
	Fulbright Scholar Award, Mahidol University, Thailand & 2022 \\
	ASTMH Travel Award & 2018 \\
	American Association of University Women Dissertation Award & 2017  \\
	ALTA Foundation Research Award & 2016 \\
	UCSF Training in Clinical Research Award for Excellence in Teaching & 2015\\
	UCSF Kwan Travel Award & 2014 \\
	American Industrial Hygiene Association  Robert Legge Scholarship & 2014 \\
	2011 European Public Health Conference Poster Award (silver) & 2011 \\
	Chadwick Trust Traveling Fellowship & 2011 \\
	Cum Laude, Georgetown University & 2010 \\
	\end{tabular}

\newpage

\section{\sc Media Coverage}

\begin{tabular}{p{4.6in}r}
  
  
	\href{https://health.ucdavis.edu/news/features/reality-bite-how-a-tiny-insect-reshaped-one-scientists-research-and-family-life/2024/12}{Reality bite: How a tiny insect reshaped one scientist's research and family life} UC Davis Health News & 12/03/24 \\

	\href{https://www.coalitionagainsttyphoid.org/the-importance-of-inclusivity-to-take-on-typhoid/}{The importance of inclusivity to take on typhoid} Coalition Against Typhoid & 03/07/24 \\
	
	\href{https://www.coalitionagainsttyphoid.org/environmental-sampling-detects-typhoid-bacteria-in-nepal/}{Environmental sampling detects typhoid bacteria in Nepal} Coalition Against Typhoid & 11/28/23 \\
	
	\href{https://www.npr.org/sections/goatsandsoda/2022/07/28/1112810432/typhoid-mutated-to-beat-antibiotics-science-is-learning-how-to-beat-those-strain}{Typhoid mutated to beat antibiotics. Science is learning how to beat those strains} NPR &  07/28/22 \\
	
	\href{https://health.ucdavis.edu/news/headlines/easier-more-accurate-method-to-detect-typhoid-infections-demonstrated-by-new-study/2022/06}{Easier, more accurate method to detect typhoid infections demonstrated by new study} UC Davis Health News & 06/29/22 \\
	
	\href{https://www.technologynetworks.com/diagnostics/news/new-technique-detects-typhoid-infections-faster-363193}{New Technique Detects Typhoid Infections Faster} Technology Networks: Diagnostics &  06/30/22 \\
	
	\href{https://scopeblog.stanford.edu/2022/07/06/tackling-typhoid-one-finger-prick-at-a-time/}{Tackling typhoid, one finger prick at a time} Stanford Medicine Scope & 07/06/22 \\
	
	\href{https://www.medgadget.com/2022/07/typhoid-detection-technique-improves-diagnostic-sensitivity.html}{Typhoid Detection Technique Improves Diagnostic Sensitivity} medgadget & 07/12/22 \\
\end{tabular}










\end{document}